Tuning Low Frequency Pulsar Searching with an Artificial Pulsar Device

### 2020-12-17 ms.tex
Updates from Overleaf

\begin{figure*}
    \centering
    \includegraphics[width=0.9\columnwidth]{dm0_fb.pdf}
    \includegraphics[width=0.9\columnwidth]{dm1_fb.pdf}
    \caption{Frequency dependent pulse profile with a $\rm DM=0$ pc cm$^{-3}$ dispersion effect applied}
    \label{fig:fb}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\columnwidth]{dm_0_trace.eps}
    \includegraphics[width=0.45\columnwidth]{dm_0.05_trace.eps}
    \caption{The voltage signal trace observed with an oscilloscope at the output terminal of the SDR transceiver. The left and the right panel show signals with ${\rm DM}=0$ pc~cm$^{-3}$ and ${\rm DM}=0.05$ pc~cm$^{-3}$, respectively. The periods of both signals are set to be $20$ ms. Note that the lower limits of the frequency range of the generated signals are 100 MHz.}
    \label{fig:osc_trace}
\end{figure}

@@

\subsubsection{Connecting the emitter and the receiver directly with a co-axis cable}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.9\columnwidth]{dm0_fb.pdf}
    \includegraphics[width=0.9\columnwidth]{dm1_fb.pdf}
    \caption{Frequency dependent pulse profile with a $\rm DM=0$ pc cm$^{-3}$ (a) and $\rm DM=0$ pc cm$^{-3}$ (b) dispersion effect applied, respectively.}
    \label{fig:fb}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\columnwidth]{dm_0_trace.eps}
    \includegraphics[width=0.45\columnwidth]{dm_0.05_trace.eps}
    \caption{The voltage signal trace (in yellow) observed with an oscilloscope at the output terminal of the SDR transceiver. The green lines are the PPS signal generated by the \textit{USRP} used to trigger the oscilloscope. The left and the right panel show signals with ${\rm DM}=0$ pc~cm$^{-3}$ and ${\rm DM}=0.05$ pc~cm$^{-3}$, respectively. The periods of both signals are set to be $20$ ms. Note that the lower limits of the frequency range of the generated signals are 100 MHz.}
    \label{fig:osc_trace}
\end{figure}

@@

\subsubsection{Connecting the emitter and the receiver directly with a co-axis cable}
We connect the emitter and receiver directly with a co-axis cable to test whether the signal generating and data acquisition sub-modules work correctly.
We show the incoherently and coherently dedispersing and folding result in Figure \ref{fig:prepfold_direct_hackrf_dm100_18} and Figure \ref{fig:cddsp_direct_hackrf_dm100_18}, respectively.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{prepfold_direct_hackrf_dm100_18.pdf}
    \caption{Incoherently dedispersing and folding result of the data acquired by \textit{HackRF} with the emitter and the receiver connected with a co-axis cable directly.}
    \label{fig:prepfold_direct_hackrf_dm100_18}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{cddsp_direct_hackrf_dm100_18.pdf}
    \caption{Coherently dedispersing and folding result of the data acquired by \textit{HackRF} with the emitter and the receiver connected with a co-axis cable directly.}
    \label{fig:cddsp_direct_hackrf_dm100_18}
\end{figure}
